Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-01-02 automatica/paper.tex
Added comments related to observer and continuous time proof
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed Description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Conrollable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

The benchmark suite employed to evaluate the proposed technique is 
composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS} and discretized with different sample time
resulting in 167 benchmarks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{DC Motor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

DC Motor benchmark describes the velocity dynamics of a basic 
brushed direct current electrical machine.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Automotive Cruise System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An automotive cruise control system is used to keep constant the speed 
of an automobile  tracking a desired speed reference, compensating 
disturbances and uncertainties related to relief and terrain.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Pendulum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A pendulum is system composed by a swinging point mass suspended from 
a frictionless pivot through a negligible mass rod.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Inverted Pendulum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An inverted pendulum is a system similar to the pendulum but the point 
mass must be equilibrated above the pivot point that is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Magnetic Suspension}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Magnetic suspension benchmark corresponds to the discrete model of a 
simple eletromagnet-ball system where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Magnetic Pointer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Magnetic pointer is a pointer, that is usually employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{1/4 Car Suspension}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The 1/4 Car Suspension benchmark corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.} the relative motion dynamics 
of a mass springer damp model that connects the car to one of its wheels.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Computer Tape Driver}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Computer Tape Drive is a computer storage device used to read and write 
data on magnetic tapes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Acrobot - Robot Manipulator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Acrobot benchmark corresponds to the model of an two-link 
underactuated robot manipulator, named Acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{High-order Systems from Chen et. al.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

These benchmarks corresponds to a series of high-order system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
 In this work, these benchmarks are used for evaluate the proposed control
 synthesis technique under critical conditions, {\it i.e.} with a greater 
 number of parameters to be considered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Continuous Stirred Tank Reactor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Flexible Beam}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A Flexible Beam is a plant usually employed in vibration studies. It is 
composed by a flexible metallic structure with piezoceramic actuators 
and sensors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Helicopter Longitudinal Motion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Helicopter Longitudinal Motion benchmark describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{USCG cutter Tampa Heading Angle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The USCG cutter Tampa Heading Angle describes the heading angle 
dynamics of a Coast Guard cutter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Voltage regulator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
in a linear model of a synchronous machine connected to an 
infinite bus.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Guidance Control System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Guidance Control System benchmark is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  in order reduction 
techniques. Guidance systems are used to determine the path of an 
autonomous vehicle movement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Satellite Attitude Control System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark describes the dynamics of a satellite attitude, 
{\it i.e.} the orientation angles. An attitude control system must 
maintain the desired orientation of satellite with respect to an 
inertial frame during all the excursion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Springer-mass damper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The springer-mass damper systems are classic models for a lot of 
mechanical systems dynamics. This benchmark describes a mass that is 
fixed to a node through a springer and moves under the action of a 
input force, damping, and elastic force.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

\textcolor{red}{Dario: Do we still need this section? Where would the continuous time proof fit?}

@@

Our benchmark suite consists of 18 MIMO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
these models are discretized with different sample times, which thus results in $167$ benchmarks
to evaluate our proposal approach.

The DC motor benchmark describes the velocity dynamics of a basic 
brushed direct current electrical machine. The automotive cruise control system 
benchmark is used to keep constant the speed of an automobile, 
tracking a desired speed reference, compensating disturbances and 
uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
a frictionless pivot through a negligible mass rod, while the inverted pendulum 
benchmark is a system similar to the pendulum, but the point 
mass must be equilibrated above the pivot point, which is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

The magnetic suspension benchmark corresponds to the discrete model of a 
simple eletromagnet-ball system, where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.
The magnetic pointer benchmark is a pointer usually employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field. The 1/4 Car Suspension benchmark corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
of a mass springer damp model, which connects the car to one of its wheels.

The Computer Tape Driver benchmark is a computer storage device used to read and write 
data on magnetic tapes. The Acrobot benchmark corresponds to the model of a two-link 
underactuated robot manipulator, named Acrobot, linearized by partial 
feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
Here, these benchmarks are used to evaluate the proposed control 
synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
to be considered.

The Continuous Stirred Tank Reactor benchmark describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor. The Flexible Beam benchmark is a plant 
usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
The Helicopter Longitudinal Motion benchmark describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The USCG cutter Tampa Heading Angle benchmark describes the heading angle 
dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
of a linear model of a synchronous machine connected to an  infinite bus.

The Guidance Control System benchmark is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
techniques. Guidance systems are used to determine the path of an 
autonomous vehicle movement.

The Satellite Attitude Control System benchmark describes the dynamics of a satellite attitude, 
{\it i.e.}, the orientation angles. An attitude control system must 
maintain the desired orientation of satellite with respect to an 
inertial frame during all the excursion. The springer-mass damper system benchmarks 
are classic models for several mechanical systems dynamics. These benchmarks describe a mass,
which is fixed to a node by means of a springer and moves under the action of a 
input force, damping, and elastic force.
